PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-14 index.qmd
adding data1

ggsave("Figures/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)

@@

ggsave("Figures/Figure1/Map_Aveiro.png",aveiro_plot,width= 10, height=10)

@@

ggsave("Figures/Figure1/Map_BB.png",width= 10, height=10)

@@

  ggsave("Figures/Figure1/Map_Morbihan.png",width= 10, height=10)

@@

Tot <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Drone_Sites.png"), interpolate = T)
BB <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_BB.png"), interpolate = T)
Mor <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Morbihan.png"), interpolate = T)
Av <- magick::image_ggplot(magick::image_read("Figures/Figure1/Map_Aveiro.png"), interpolate = T)

@@

ggsave("./Figures/Fig1_Map_Drone_Sites.png",a, width= 10, height=10, dpi = 800)

@@

save_as_image(flx1, "Figures/table_flights.png", res = 300)
```

@@

knitr::include_graphics("Figures/table_flights.png")
```

@@

imglist<-
  data.frame(path = list.files(pattern = ".tif", recursive = T, full.names = T)) %>% 
  mutate(folder = case_when(str_detect(path, "Data") ~ "Input",
                            TRUE ~ "Output"),
         alt = case_when(str_detect(path, "high") ~ "high",
                         str_detect(path, "High") ~ "high",
                         TRUE ~ "low"),
         site = case_when(str_detect(path, "Gafanha") ~ "Gafanha",
                          str_detect(path, "Arz") ~ "Arz",
                          TRUE ~ "Duer"),
         type = case_when(str_detect(path, "pred") ~ "Pred",
                          str_detect(path, "NDVI") ~ "NDVI",
                          str_detect(path, "Pred") ~ "Pred",
                          TRUE ~ "ortho"),
         resampled = case_when(str_detect(path, "resampled") ~ "TRUE",
                          TRUE ~ "FALSE"),
         correction = case_when(str_detect(path, "corrected_per_bands") ~ "Bands",
                          str_detect(path, "corrected.tif") ~ "lm_all",
                          TRUE ~ "NA")) %>% 
  dplyr::filter(alt != "NA",
                !str_detect(path,".xml"),
                !str_detect(path,".enp"))

gaf_low_multi<- imglist %>% 
  filter(site == "Gafanha",
         alt == "low",
         type == "ortho",
         resampled == "FALSE",
         folder == "Input") %>%
  slice(1) %>% 
  pull(path) %>%
  rast() 
 names(gaf_low_multi)<-c(paste0("B",c(1:10)))

 Gafanha_low_pred<-"./Data/image/prediction/NewPreds/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
     rast()
 names(Gafanha_low_pred)<-"pred"

@@

ggsave("Figures/Spectral_shapes.png",spectra, bg = "transparent",  height = 2, width = 3, dpi = 2000)

sp <- image_ggplot(magick::image_read("Figures/Spectral_shapes.png"), interpolate = T)

@@

ggsave("Figures/Spectral_shapes_total.png",plot, height = 7, width = 10, dpi = 800)
```

>>>>

ggsave("Figures/High_res/Figure1/Map_Drone_Sites.png",p1,width= 10, height=10)

@@

ggsave("Figures/High_res/Figure1/Map_Aveiro.png",aveiro_plot,width= 10, height=10)

@@

ggsave("Figures/High_res/Figure1/Map_BB.png",width= 10, height=10)

@@

  ggsave("Figures/High_res/Figure1/Map_Morbihan.png",width= 10, height=10)

@@

Tot <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Drone_Sites.png"), interpolate = T)
BB <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_BB.png"), interpolate = T)
Mor <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Morbihan.png"), interpolate = T)
Av <- magick::image_ggplot(magick::image_read("Figures/High_res/Figure1/Map_Aveiro.png"), interpolate = T)

@@

ggsave("./Figures/High_res/Figure1/Fig1_Map_Drone_Sites.png",a, width= 10, height=10, dpi = 800)
```

@@

save_as_image(flx1, "Figures/High_res/Table1/table_flights.png", res = 300)
```

@@

knitr::include_graphics("Figures/High_res/Table1/table_flights.png")
```

@@

gaf_low_multi<- "./Data/BiCOME_Flights/Aveiro/Aveiro_MULTI_12m_ortho_1801.tif" %>% 
  rast()

names(gaf_low_multi)<-c(paste0("B",c(1:10)))

 Gafanha_low_pred<-"./Data/image/prediction/AveiroLowPrediction_nnNewStanRawMetrics_Preds_NoXantho_7.tif" %>% 
     rast()
 names(Gafanha_low_pred)<-"pred"

@@

ggsave("Figures/High_res/Figure2/Spectral_shapes.png",spectra, bg = "transparent",  height = 2, width = 3, dpi = 2000)

sp <- image_ggplot(magick::image_read("Figures/High_res/Figure2/Spectral_shapes.png"), interpolate = T)

@@

ggsave("Figures/High_res/Figure2/Spectral_shapes_total.png",plot, height = 7, width = 10, dpi = 800)
```
